Benchmarking Python Deep Learning Frameworks\\ for Language Modeling on GPUs

### 2016-12-14 paper/main.tex

\subsection{Implementation \& Hyperparameters}
\ms{Add equations/words to explain what a neural LM does.}
In our experiments, we optimized for a standard language modeling objective: \textit{cross-entropy}. The built-in cross-entropy loss functions in each framework were slightly different, which could potentially affect the number of iterations required for convergence. \ms{TODO: add github somewhere}

>>>>

\subsection{Implementation \& Hyperparameters}
We implemented the same recurrent neural language model in each framework. The model consists of a matrix of input word embeddings, which are passed through a RNN to get predicted word embeddings, which are compared via a loss function to a corresponding set of output embeddings. All these elements are available in all frameworks (in Theano's case, the RNN is provided by the Keras wrapper). Our implementations are made available on GitHub.\footnote{\url{https://github.com/lucylin/neural-benchmarks}}
In our experiments, we optimized for a standard language modeling objective: \textit{cross-entropy}. The built-in cross-entropy loss functions in each framework were slightly different, which could potentially affect the number of iterations required for convergence.
